---
title: "ISM 5570 Data Mining and Analytics - Fall 2020"
output: 
  html_document:
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(fontawesome)
library(kableExtra)
knitr::read_chunk('global.R')
```

```{r global, echo=FALSE}
```

This is an introductory data science course, presuming no prior experience of coding and data analytics. Students will learn essential skills for data-driven decision making, including data wrangling, modeling, visualization, and effective communication with data. Focusing on the R language, the course makes an extensive use of hands-on exercises. The access to a laptop/desktop is required for this course.

```{r ddd, echo=FALSE}
icon <- paste0("<a href=\"", "kyunghee.lee@wayne.edu", "\">", as.character(fa(name = "envelope", fill = "steelblue")), "</a>")
df <- tibble(
  c('Instructor', 'Office', 'Format'),
  c(paste0('Kyunghee Lee ', icon), 437, 'Online')
)
knitr::kable(df, escape = F, col.names=NULL) %>%
  kable_styling(bootstrap_options = "striped")
```

#### Texts are freely available
* [Grolemund, Garrett, and Wickham, Hadley. R for data science, 1st Edition, O'Reilly Media](https://r4ds.had.co.nz/)  
* [Irizarry, Rafael, Introduction to Data Science, 1st Edition, Chapman and Hall/CRC](https://rafalab.github.io/dsbook/)

#### Review [Course Policies](policies.html)

Each module starts at 6:00 pm on the date shown in the schedule. All the evaluations (exercise, homework, exam) must be submitted by 5:59 pm on their due dates before the next week module starts. The syllabus and policies are preliminary and always subject to change.

```{r schedule, echo=FALSE}
addLink <- function(link, img, color) {
  paste0("<a href=\"", link, "\">", as.character(fa(name = img, fill = color)), "</a>")
}
noLink <- function(img, color) {
  fa(name = img, fill = color)
}

addicon <- function(i, img){
  if (is.na(i)==FALSE) {
    addLink(i, img, 'steelblue')
  }
  else {
    noLink(img, 'lightblue')
  }
}

slide <- sapply(slide_links, addicon, img='folder')
dc <- sapply(dc_links, addicon, img='flask')
hw <- sapply(hw_links, addicon, img='code')
exam <- sapply(exam_links, addicon, img='edit')

df <- tibble(
  Date=date,
  Topic=topic,
  Slide=slide,
  Ex.=dc,
  HW=hw,
  Exam=exam
)
# knitr::kable(df) 
knitr::kable(df, escape = F) %>%
  kable_styling(bootstrap_options = "striped", font_size = 18)
```
