---
title: "ISM 5570 Data Mining and Analytics - Winter 2021"
output: 
  html_document:
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(fontawesome)
library(kableExtra)
knitr::read_chunk('global.R')
week <- 14
```

```{r global, echo=FALSE}
```

This is an introductory data science course, presuming no prior experience of coding and data analytics. Students will learn essential skills for data-driven decision making, including data wrangling, visualization, modeling, basic machine learning algorithms, and effective communication with data. Focusing on the R language, the course makes an extensive use of hands-on exercises. **The access to a laptop/desktop is required in this course.**

```{r ddd, echo=FALSE}
icon <- paste0("<a href=\"", "kyunghee.lee@wayne.edu", "\">", as.character(fa(name = "envelope", fill = "steelblue")), "</a>")
df <- tibble(
  c('Instructor', 'Office', 'Format'),
  c(paste0('Kyunghee Lee ', icon), 437, 'Online')
)
knitr::kable(df, escape = F, col.names=NULL) %>%
  kable_styling(bootstrap_options = "striped")
```

#### Texts are freely available
* [Grolemund, Garrett, and Wickham, Hadley. R for data science, 1st Edition, O'Reilly Media](https://r4ds.had.co.nz/){target="_blank"}
* [Irizarry, Rafael, Introduction to Data Science, 1st Edition, Chapman and Hall/CRC](https://rafalab.github.io/dsbook/){target="_blank"}

#### Tech
* [DataCamp Tutorial](./dc_tutorial.html){target="_blank"}
* [R/Rstudio](./lab/lab-01/lab-01-hello-r.html){target="_blank"}
* [Lockdown Browser & Respondus Monitor](./lockdown_browser.html){target="_blank"}

#### Review [Course Policies](policies.html){target="_blank"}

Each module starts at 6:00 pm on the date shown in the schedule. All the evaluations (exercise, homework, exam) must be submitted by 5:59 pm on their due dates before the next week module starts. The syllabus and policies are preliminary and always subject to change.

***The midterm and final exams will be during the weekend of the specified week, from Saturday 9:00 AM to Sunday 11:59 PM.** 

```{r schedule, echo=FALSE}
addLink <- function(link, img, color) {
  paste0("<a href=\"", link, "\" target=\"_blank\">", as.character(fa(name = img, fill = color)), "</a>")
  # paste0("<a href=\"", link, "\">", as.character(fa(name = img, fill = color)), "</a>")
}
noLink <- function(img, color) {
  fa(name = img, fill = color)
}

addicon <- function(i, img){
  if (is.na(i)==FALSE) {
    addLink(i, img, 'steelblue')
  }
  else {
    noLink(img, 'lightblue')
  }
}

publish <- function(list){
  for(i in n){
    if(i > week){
      list[i] <- NA
    }
  }
  list
}

lecture <- sapply(publish(lecture_links), addicon, img='folder')
lab <- sapply(publish(lab_links), addicon, img='flask')
dc <- sapply(publish(dc_links), addicon, img='code')
hw <- sapply(publish(hw_links), addicon, img='edit')
exam <- sapply(publish(exam_links), addicon, img='calendar-check')

df <- tibble(
  Date=date,
  Topic=topic,
  Lecture=lecture,
  Lab=lab,
  Ex.=dc,
  HW=hw,
  Exam=exam
)
# knitr::kable(df) 
knitr::kable(df, escape = F) %>%
  kable_styling(bootstrap_options = "striped", font_size = 18)
```
