---
title: "Test slide - PPT from R Markdown"
subtitle: "Kyunghee Lee, PhD"
output: 
  powerpoint_presentation: 
    reference_doc: template.pptx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
# Section Header

## R Markdown

### Subheader

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Two column contents

:::::::::::::: {.columns}
::: {.column}
contents1...
:::
::: {.column}
contents2...
:::
::::::::::::::

## Markdown style

*italic*  
**bold**  
~~strikeout~~  
~subscript~  
^superscript^  
[small caps]{.smallcaps}   
`verbatim`  

1. Numbered list
* Unnumbered list

$math-expression$
$$math-equation$$
[link](target) 

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

