---
title: "Homework 1 - Data wrangling and visualization"
author: "Enter Your Name"
output: 
  html_document:
    theme: cosmo
    toc: TRUE
    toc_float: TRUE
    code_download: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


In this homework, ...

which one is the worst airline.

Change the author name to yours


```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(nycflights13)
```


# Question 1

- Q1-1. Remove the columns `year` from your data frame (`flights1`) [Hint: Reassign a data frame excluding the variables. You may want to use negative index]
```{r label='q1-1'}
flights %>%
  select(-year)
```

- Q1-2. Add a new variable, total_delay, which is the sum of `dep_delay` and `arr_delay`, and sort your data frame in descending order of total_delay. Save the output as a new data frame `flight1`
```{r label='q1-2'}
flights1 <- flights %>%
  mutate(total_delay = dep_delay + arr_delay) %>% 
  arrange(desc(total_delay))
```

- Q1-3. Use `flight1` data frame and draw box plots of total delay separately by carriers

```{r}
ggplot(flights1, aes(x=carrier, y=total_delay)) + 
  geom_boxplot()
```

