---
title: "Homework 1 - Data wrangling and visualization"
author: "Kyunghee"
output: 
  html_document:
    theme: cosmo
    toc: TRUE
    toc_float: TRUE
    code_download: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Release: `r due_hw$release[1]`**  
**Due: `r due_hw$due[1]`**

In this homework, ...

Change the author name to yours


```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(nycflights13)
```


# Question 1

- Q1-1. Remove the columns `year` from your data frame (`flights1`) [Hint: Reassign a data frame excluding the variables. You may want to use negative index]
```{r label='q1-1'}
flights %>%
  select(-year
```

- Q1-2. Add a new variable, total_delay, which is the sum of `dep_delay` and `arr_delay`, to your data frame (`flights1`). Sort your data frame (`flights1`) in descending order of total_delay, and save it as a new data frame `flight2`
```{r label='q1-2'}
flights1 <- flights %>%
  mutate(total = arr_delay) %>% 
  arrange(desc(total))
```

