---
title: "Datacamp Exercise 2"
subtitle: "Intermediate R"
output: 
  html_document: 
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE}
knitr::read_chunk('../global.R')
```

```{r global, echo=FALSE}
```

**Release: `r due_dc$release[2]`**  
**Due: `r due_dc$due[2]`**

Intermediate R is the next stop on your journey in mastering the R programming language. In this R training, you will learn about conditional statements, loops, and functions to power your own R scripts. Next, make your R code more efficient and readable using the apply functions. Finally, the utilities chapter gets you up to speed with regular expressions in R, data structure manipulations, and times and dates. This course will allow you to take the next step in advancing your overall knowledge and capabilities while programming in R.

* Go here to start: [https://learn.datacamp.com/courses/intermediate-r](https://learn.datacamp.com/courses/intermediate-r){target="_blank"}
* Complete **the entire course**
* If you haven't signed up, click [here](../dc_tutorial.html) to create an account (you must use `wayne.edu` email to join)
* **The due date** is specified in this page as well as your DataCamp dashboard. Be sure to make it in time!
