---
title: "Datacamp Exercise 4"
subtitle: "Data wrangling"
output: 
  html_document: 
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE}
knitr::read_chunk('../global.R')
```

```{r global, echo=FALSE}
```

**Release: `r due_dc$release[4]`**  
**Due: `r due_dc$due[4]`**

In this chapter, you'll learn to do three things with a table: filter for particular observations, arrange the observations in a desired order, and mutate to add or change a column. You'll see how each of these steps allows you to answer questions about your data.

* Go here to start: [https://campus.datacamp.com/courses/introduction-to-the-tidyverse/data-wrangling-1](https://campus.datacamp.com/courses/introduction-to-the-tidyverse/data-wrangling-1){target="_blank"}
* If you haven't signed up, click [here](../lecture/w01-welcome/w01-welcome.html#_DataCamp_Tutorial) to create an account (you must use `wayne.edu` email to join)
* **The due date** is specified in this page as well as your DataCamp dashboard. Be sure to make it in time!
