---
title: "Lab 04 - Data wrangling"
author: "Kyunghee Lee"
output: 
  html_document:
    theme: cosmo
    toc: TRUE
    toc_float: TRUE
    code_download: TRUE
link-citations: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Below is the code we use from the lecture, plus some exercise questions. The RMD file is on `Code` tab on the top. You can either `Knit` the entire document to produce a html doc, `Run All` to only run R codes, or run one R chunk at a time by clicking the play button. Remember that your code must be inside **R chunks**. Otherwise, your computer would just treat your code as plain text and won't run it. If you're not sure what you should do, please refer to the instructions and video in [Lab 1](../lab-01/lab-01-hello-r.html).

There is a couple of exercises you can play with. For each question, I put a R chunk and a line saying `# write your code below this comment line` in case you don't know where to start. You're welcome to create as many R chunks and do experiments as you like.

# Data: Hotel bookings

As always, let's call `tidyverse` first.
```{r warning=FALSE, message=FALSE}
library(tidyverse)
```

Unlike the other prior labs where we import data from packages, we're going to import a csv file this time. To do this, you first need to download `hotels.csv` from [this download link](https://khlee42.github.io/datamining/lab/lab-04/hotels.csv){target="_blank"} and save it in the same directory where you downloaded this RMD file. Both RMD and csv file must be in the same directory!

```{r message=FALSE}
hotels <- read_csv("hotels.csv")
```

Once you've loaded the data, take a look at it using `names` (or `glimpse`, `head`, or `str`). A brief description about the data: 

- Data from two hotels: one resort and one city hotel
- Observations: Each row represents a hotel booking
- Goal for original data collection: Development of prediction models to classify a hotel booking's likelihood to be cancelled ([Antonia et al., 2019](https://www.sciencedirect.com/science/article/pii/S2352340918315191#bib5))

```{r message=FALSE}
names(hotels)
```

# Manipulate columns

## `select` to keep variables

To select a variable, use `%>%` and `select` function. 
```{r}
hotels %>%
  select(hotel)
```

To select multiple variables, simply list the columns inside:
```{r}
hotels %>% 
  select(hotel, lead_time, agent)
```


## `select` to exclude variables

You can also select which variable to **exclude**. All you need is `-` sign and put it in front of the variable to exclude. The code below is to select all variables except agent.
```{r}
hotels %>%
  select(-agent) #<<
```

## `select` variables with certain characteristics

`select` can also do search variable names for specific keywords. The below is to select variables whose name **starts** with "arrival":
```{r}
hotels %>%
  select(starts_with("arrival")) #<<
```
And, this one is to select variables whose name **ends** with "type":
```{r}
hotels %>%
  select(ends_with("type")) #<<
```

## `mutate` to add a new variable

`mutate` is used to create a new variable in a data set. Let's start with a simple one: copy the children variable and add it to a new variable named children2:
```{r}
hotels %>% 
  mutate(children2 = children) %>% 
  select(children, children2)
```
Instead of copy, let's make a variable that requires some calculation. The below is to create a variable called "little_ones" that is the sum of "children" and "babies":
```{r}
hotels %>%
  mutate(little_ones = children + babies) %>% 
  select(children, babies, little_ones) %>% 
  arrange(desc(little_ones))
```
The arrange function at the end is used to sort the data in the descending order of "little_ones."

# Manipulate rows

## `slice` for certain row numbers
`slice` requires two arguments: the starting position and the end position. e.g., to slice the first five row, the starting position is one and the end position is 5:
```{r}
hotels %>%
  # slice the first five rows  # this line is a comment
  #select(hotel) %>%           # this one doesn't run
  slice(1:5)                   # this line runs
```
Notice that there are two additional lines between `hotels` and `slice()`. They are comments as they come after `#`. Comments are not executable, and won't affect your code output. You can leave as many comments as you want.

To slice the last five rows, first we need to figure out the index for the last row in the data. You can get the number from `nrow()` and use that number in `slice()` to identify the starting and end positions:
```{r}
# last five
last_row <- nrow(hotels)         # nrow() gives the number of rows in a data frame
hotels %>%
  slice((last_row - 4):last_row) #<<
```

## `filter` to select a subset of rows

Using `filter()`, you can filter observations with any conditions you want, like equality condition:
```{r}
# bookings in City Hotels
hotels %>%
  filter(hotel == "City Hotel")
```

many conditions at once:
```{r}
hotels %>%
  filter( 
    adults == 0,  
    children >= 1 
    ) %>% 
  select(adults, babies, children)
```

Or even more complex conditions that involve logical operators:

```{r}
# bookings with no adults and some children or babies in the room
hotels %>%
  filter( 
    adults == 0,     
    children >= 1 | babies >= 1     # | means or  #<<
    ) %>%
  select(adults, babies, children)
```

This is a list of the logical operators in R for your reference.

operator    | definition                   || operator     | definition
------------|------------------------------||--------------|----------------
`<`         | less than                    || `x & y`      | `x` AND `y`
`<=`        |	less than or equal to        || `x`&nbsp;&#124;&nbsp;`y`   | `x` OR `y` 
            |                              || `!x`         | not `x`
`>`         | greater than                 || `is.na(x)`   | test if `x` is `NA`
`>=`        |	greater than or equal to     || `!is.na(x)`  | test if `x` is not `NA`
`==`        |	exactly equal to             || `x %in% y`   | test if `x` is in `y`
`!=`        |	not equal to                 || `!(x %in% y)`| test if `x` is not in `y`

## Select unique rows

```{r}
hotels %>% 
  distinct(market_segment)
```


# Explore data

## `count` to create frequency tables

```{r}
# alphabetical order by default
hotels %>%
  count(market_segment) #<<
```

## `count` and `arrange`

```{r}
# ascending frequency order
hotels %>%
  count(market_segment) %>%
  arrange(n) #<<
```

## `summarise` for summary stats
`summarise` can be used for multiple summary statistics as well

```{r}
hotels %>%
  summarise(
    min_adr = min(adr),
    mean_adr = mean(adr),
    median_adr = median(adr),
    max_adr = max(adr)
    )
```
## `group_by` for grouped operations
```{r}
# mean average daily rate for all booking at city and resort hotels
hotels %>%
  group_by(hotel) %>% #<<
  summarise(mean_adr = mean(adr))
```


# Exercise

1. Add a variable "little_ones" that is the sum of "children" and "babies" to "hotels" data frame
```{r}
# write your code below this comment line


```

2. Choose booking records with more than one "little_ones", select the three columns ("hotel", "country", "little_ones"), and save the output as "booking_with_littleone"
```{r}
# write your code below this comment line


```
3. Using "booking_with_littleone", calculate the average number of little_ones (hint: `summarise()`)
```{r}
# write your code below this comment line

```

4. Using "booking_with_littleone", calculate the average number of little_ones by country [hint: `group_by()`]
```{r}
# write your code below this comment line

```

5. Using "booking_with_littleone", count the number of observations for each value of "little_ones" and save the output as "freq_by_little" [hint: use `count()` to create a frequency table based on "little_ones"]

```{r}
# write your code below this comment line


```

6. Using "freq_by_little", calculate the probability for each value of "little_ones" [hint: prop = n / sum(n) ]
```{r}
# write your code below this comment line


```

