---
title: "Lab 02 - R essentials"
author: "Kyunghee Lee"
output: 
  html_document:
    theme: cosmo
    toc: TRUE
    toc_float: TRUE
    code_download: TRUE
link-citations: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Below is the code we use from the lecture 2, plus some exercise questions. The RMD file is on `Code` tab on the top. You can either `Knit` the entire document to produce a html doc, `Run All` to only run R codes, or run one R chunk at a time by clicking the play button.

Remember that your code must be inside **R chunks**. We've learned from the lecture 2 that R codes must be inside of the R chunk, surrounded by three backticks. Otherwise, your computer would just treat your code as plain text and won't run it.

There is a couple of exercises you can play with. For each question, I put a R chunk and a line saying `# write your code below this comment line` in case you don't know where to start. You're welcome to create as many R chunks and do experiments as you like.


# Variable

## Assign value `<-`

You can assign a value to a variable and use it by referring the name. We use `<-` sign for this.

```{r}
a <- 12
b <- 157
a
b
```

Store the result in a variable

```{r}
c <- a*b
c
```

## Data type

R can handle a variety of data including **numeric, logical, character.**

```{r}
title <- "silicon valley"
season <- 5
episode <- 4
rating <- 4.8
is_show_finished <- TRUE
```

## What's the data type?

Use `class()` function to find out

```{r}
class(title)
class(season)
class(rating)
class(is_show_finished)
```

Boolean values (TRUE or FALSE) are **logical**

# Vector

## When to use vector?

To store more than one value, we need the combine function `c()` to create a vector

```{r}
numeric_vector <- c(5,6)
numeric_vector
character_vector <- c("season","episode")
character_vector
```

## Name vector elements `names()`

```{r}
names(numeric_vector) <- c("season", "ep")
numeric_vector
```

Or, we could use `character_vector` already defined to do the same thing
```{r}
names(numeric_vector) <- character_vector
numeric_vector
```

Notice the name of the second column has changed from "ep" to "episode"

## Vector calculation
### Calculation between two vectors

We can do arithmetic calculations on vectors


```{r}
s1_rating_vector <- c(3.4, 2.8, 1, 5, 4.5)
s2_rating_vector <- c(5, 4.7, 2, 3.4, 2.2)
episode_vector <- c("ep1", "ep2", "ep3", "ep4", "ep5")
names(s1_rating_vector) <- episode_vector
names(s2_rating_vector) <- episode_vector
s1_rating_vector + s2_rating_vector
s1_rating_vector * s2_rating_vector
```

- Important: the numbers of elements in the vectors must be the same

```{r}
s3_rating_vector <- c(1, 3.2, 5)
s1_rating_vector + s3_rating_vector
```

### Calculation within a vector

```{r}
sum(s1_rating_vector) # sum
prod(s1_rating_vector) # product
mean(s1_rating_vector) # average
sd(s1_rating_vector) # standard deviation
```

## Compare rating by episode

```{r}
s1_rating_vector > s2_rating_vector
```

```{r}
s1_rating_vector < s2_rating_vector
```

```{r}
s1_rating_vector == s2_rating_vector
```

- `>`, `<`, `==` are called **logical comparison operator**. More on this later!

## Exercise 1

1. What's the average rating for each season?

```{r}
# write your code below this comment line



```


2. Is the season 1 has a higher average rating than the season 2?

```{r}
# write your code below this comment line


```

3. What's the data type of `is_s1_better_than_s2`? [Hint: use class()]

```{r}
# write your code below this comment line


```


## Vector selection

### Select vector element with index

```{r}
s1_ep1 <- s1_rating_vector[1]
s1_ep1
s1_ep3 <- s1_rating_vector[3]
s1_ep3
```

```{r}
s1_ep1_and_3 <- s1_rating_vector[c(1,3)]
s1_ep1_and_3
```

```{r}
s1_ep1_through_3 <- s1_rating_vector[1:3]
s1_ep1_through_3
```


### Select vector element with name

```{r}
s1_rating_vector
s1_ep1 <- s1_rating_vector["ep1"]
s1_ep1
s1_ep1_and_3 <- s1_rating_vector[c("ep1", "ep3")]
s1_ep1_and_3
```

### Select vector element with condition

Which episode has rating > 4?

```{r}
s1_rating_vector
s1_ep_above_4 <- s1_rating_vector > 4
s1_ep_above_4
s1_rating_vector[s1_ep_above_4]
```

# Data frame

## When to use data frame?

- A single value `r emo::ji('right_arrow')` variable
- More than one value `r emo::ji('right_arrow')` vector
- Multiple vectors `r emo::ji('right_arrow')` data frame

Use `data.frame()` function to store a data set comprising of different data types
```{r}
s1_rating_vector <- c(3.4, 2.8, 1, 5, 4.5)
s2_rating_vector <- c(5, 4.7, 2, 3.4, 2.2)
episode_vector <- c("ep1", "ep2", "ep3", "ep4", "ep5")
rating_df <- data.frame(episode_vector, s1_rating_vector, s2_rating_vector)
```


## View data frame

```{r}
head(rating_df) # first part of data
str(rating_df) # structure
```

## Name columns

```{r}
rating_df <- data.frame(episode=episode_vector, 
                        season1=s1_rating_vector, 
                        season2=s2_rating_vector)
head(rating_df)
```

## Select columns

```{r}
rating_df$episode
rating_df$season1
rating_df$season2
```

## Exercise 2

1. Create a numeric vector named `s3_rating_vector` with the five values: 2.3, 4,6, 5.6, 2.0, 3.0

```{r}
# write your code below this comment line

```

2. What's the average of `s3_rating_vector`?

```{r}
# write your code below this comment line

```

3. Create a data frame named `rating_df2` that includes the four vectors: episode_vector, s1_rating_vector, s2_rating_vector, and s3_rating_vector

```{r}
# write your code below this comment line

```

4. What's the average rating of season 2?

```{r}
# write your code below this comment line

```

5. What's the min rating of season 3? [Hint: use min()]

```{r}
# write your code below this comment line

```



